Supplementary Information -- Morphological convergence as on-line lexical analogy

### 2020-02-18 supplementary_information/si.Rnw
after Clays first round of comments

# setting up columns in baseline and post-test data
baseline = baseline %>% 
  dplyr::mutate(
    r_baseline_mgl_features = scales::rescale(baseline_mgl_features), # rescale regularity weights
    r_baseline_gcm_features = scales::rescale(baseline_gcm_features),
  )

test2 = test2 %>% 
  dplyr::mutate(
    verb_baseline_average = baseline_av - mean(baseline_av, na.rm = T), # center verb average
    participant_prereg_average = pre_reg_av - mean(pre_reg_av, na.rm = T), # center participant average
    bot_lexical_typicality = dplyr::case_when( # set factor levels used in paper, order factor
        lex_typicality == 'typical' ~ 'typical',
        lex_typicality == 'random' ~ 'random',
        lex_typicality == 'atypical' ~ 'reversed'
      ) %>% 
      factor(levels = c('typical', 'random', 'reversed')),
    bot_regularisation_rate = reg_rate %>% # order factor
      factor(levels = c('nc', '-40%', '+40%')),
    r_baseline_mgl_features = scales::rescale(baseline_mgl_features), # scale regular weights
    r_baseline_gcm_features = scales::rescale(baseline_gcm_features),
    r_individual_mgl_features = scales::rescale(individual_mgl_features),
    r_individual_gcm_features = scales::rescale(individual_gcm_features),
    gcm_score_diff = r_individual_gcm_features - r_baseline_gcm_features, # calculate score diff
    mgl_score_diff = r_individual_mgl_features - r_baseline_mgl_features
  )

@@

Sections (\ref{appendixgcm}) and (\ref{appendixmgl}) also appear in the main text of  R\'acz et al. (2020), as Appendices A and B. However, this material is included here so that this Supplement can serve as a standalone document for readers who are interested in the technical details of our study.

@@

splive_gcm = test2 %>% 
  dplyr::filter(word == 'splive') %>% 
  dplyr::pull(r_baseline_gcm_features) %>% 
  unique %>% 
  round(2)

@@

test2 %>% 
  dplyr::filter(word == 'splive') %>% 
  dplyr::select(baseline_mgl_features,r_baseline_mgl_features) %>% 
  dplyr::distinct()

@@

In the model in Table 5 in the main text, repeated here as Table \ref{regressiontable1}, we elect to mean center continuous variables to counteract collinearity that becomes evident when including the interaction between and {\em lexical typicality} .  Although some debate exists regarding the practice of transforming variables \citep{belsley1991conditioning,echambadi2007mean}, centering variables is common practice to remove nonessential ill conditioning, that is, relationships that inevitably exist between main and product terms \citep{aiken1991multiple,jaccard2003interaction, jaeger2008categorical}. We note that if {\em verb baseline mean} is {\em not} centered, collinearity is high (VIF=15.79) in this model. A non-centered model also yields a significant main effect for {\em lexical typicality}, with increased post-test regularization in the random and reversed conditions. However, we elect to take a more conservative approach by not including a potentially spurious main effect. Note that other than this main effect difference, models with and without centering yield results that are qualitatively indistinguishable; all other main effects and interactions are present in either case. The collinearity for the centered model (Table 5 in the main text) is acceptable, with a maximum VIF score of 2.9.

@@

We fit the Celex-GCM and the Celex-MGL on the baseline data to see how well they predict regularisation responses by the baseline participants. The Celex-MGL outperforms the Celex-GCM, if slightly. Both models contribute independently to explaining variation in the data.

@@

C_baseline_mgl_features = with(baseline, Hmisc::somers2(r_baseline_mgl_features,regular)['C']) %>% 
  round(3)
C_baseline_gcm_features = with(baseline, Hmisc::somers2(r_baseline_gcm_features,regular)['C']) %>% 
  round(3)

# get correlation between mgl and gcm scores in baseline
mgl_gcm_cor = baseline %>% 
  dplyr::distinct(word,r_baseline_mgl_features,baseline_gcm_features) %>% 
  dplyr::summarise(
    cor = cor(r_baseline_mgl_features,baseline_gcm_features)
  ) %>% 
  dplyr::pull() %>% 
  round(3)

@@

The concordance indices of the Celex-MGL (\Sexpr{C_baseline_mgl_features}) and the Celex-MGL (\Sexpr{C_baseline_gcm_features}) on the baseline data are similar, with some edge retained by the MGL, as in the case of \citep{albright2003rules}. Our concordance indices are calculated using the somers2 function in R's \texttt{Hmisc} package \citep{harrell2014hmisc}.

@@

# simple baseline words data frame
baseline_words = baseline %>% 
  dplyr::distinct(word, r_baseline_mgl_features, r_baseline_gcm_features)

# fitting models 1 and 2 on it
celex_m1 = lm(r_baseline_gcm_features ~ 1 + r_baseline_mgl_features, data = baseline_words)
celex_m2 = lm(r_baseline_mgl_features ~ 1 + r_baseline_gcm_features, data = baseline_words)

# getting residuals from models and putting them back in this data frame
baseline_words = baseline_words %>% 
  dplyr::mutate(
    r_baseline_gcm_features_residual = resid(celex_m1),
    r_baseline_mgl_features_residual = resid(celex_m2)
  )

# joining it with entire baseline data
baseline = left_join(baseline, baseline_words, by = c("word", "r_baseline_mgl_features", "r_baseline_gcm_features"))

# fitting models 3 and 4
celex_m3 = glmer(regular ~ 
                1 + r_baseline_mgl_features + r_baseline_gcm_features_residual + 
                (1 + r_baseline_mgl_features + r_baseline_gcm_features_residual | subject), 
                data = baseline, 
                family = binomial ( link = logit ),
                control=glmerControl(optimizer="bobyqa"))

celex_m4 = glmer(regular ~ 
                1 + r_baseline_gcm_features + r_baseline_mgl_features_residual + 
                (1 + r_baseline_gcm_features + r_baseline_mgl_features_residual | subject), 
                data = baseline, 
                family = binomial ( link = logit ),
                control=glmerControl(optimizer="bobyqa"))

@@

<<celex_resid1, echo=F,eval=T, results=tex>>=
load('models/si_celex_m3.rda')
print(xtable::xtable(summary(celex_m3)$coef, digits = 3, label = 'resid1', caption = 'MGL scores and GCM residuals, baseline data'))
@

<<celex_resid2, echo=F,eval=T, results=tex>>=
load('models/si_celex_m4.rda')
print(xtable::xtable(summary(celex_m4)$coef, digits = 3, label = 'resid2', caption = 'GCM scores and MGL residuals, baseline data'))
@

@@

We fit the Celex-GCM,the Celex-MGL, as well as the Individual-GCM and the Individual-MGL on the post-test data. Recall that the Celex-based models were trained on verbs in Celex. The individual-based models were trained for each participant, on Celex verbs as well as the co-player's responses in the ESP test. They were tested on the post-test for each participant, individually.

@@

First, we calculated concordance indices for the Celex- and individual-models on the post-test data of the ESP experiment.

@@

# C_baseline_mgl_features # celex-mgl on baseline
# C_baseline_gcm_features # celex-gcm on baseline

C_test2_baseline_mgl_features = with(test2, Hmisc::somers2(r_baseline_mgl_features,resp_post_reg)['C']) %>% round(3)
C_test2_baseline_gcm_features = with(test2, Hmisc::somers2(r_baseline_gcm_features,resp_post_reg)['C']) %>% round(3)
C_test2_individual_mgl_features = with(test2, Hmisc::somers2(r_individual_mgl_features,resp_post_reg)['C']) %>% round(3)
C_test2_individual_gcm_features = with(test2, Hmisc::somers2(r_individual_gcm_features,resp_post_reg)['C']) %>% round(3)

@@

Table \ref{modellingsummary} summarizes the concordance indices between our data and the various categorization models. The \textsc{Celex}-MGL, outperforms the \textsc{Celex}-GCM on the post-test data to some extent, much like in the case of our baseline data. The individual-GCM considerably improves on the \textsc{Celex}-GCM in terms of explaining the post-test data. The individual-MGL also improves on the \textsc{Celex}-MGL, but to a lesser extent.

@@

    \centering
    \begin{tabular}{lllll}
            & training data & method & test data & C\\
            \hline
\textsc{Celex}-GCM & real verbs & `analogy' & verbs in baseline &\Sexpr{C_baseline_gcm_features }\\
\textsc{Celex}-MGL & real verbs & `rules' & verbs in baseline &\Sexpr{C_baseline_mgl_features }\\ \hline
\textsc{Celex}-GCM & real verbs & `analogy' & verbs in post-test &\Sexpr{C_test2_baseline_gcm_features}\\
individual-GCM & real verbs + verbs seen in ESP & `analogy' & verbs in post-test &\Sexpr{C_test2_individual_gcm_features}\\

@@

indiv_m5 = glmer(resp_post_reg ~
    1 + r_baseline_gcm_features + gcm_score_diff + participant_prereg_average + 
    (1 + r_baseline_gcm_features + gcm_score_diff | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

@@

indiv_m6 = glmer(resp_post_reg ~ 
    1 + r_baseline_mgl_features + mgl_score_diff + participant_prereg_average  + 
    (1 + r_baseline_mgl_features + mgl_score_diff | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

@@

load('models/si_indiv_m5.rda')
print(xtable::xtable(summary(indiv_m5)$coef, digits = 3, label = 'indiv1', caption = 'Celex-GCM and individual score difference, post-test data'))

@@

<<indiv_diff2, echo=F,eval=T, results=tex>>=
load('models/si_indiv_m6.rda')
print(xtable::xtable(summary(indiv_m6)$coef, digits = 3, label = 'indiv2', caption = 'Celex-MGL and individual score difference, post-test data'))
@

@@

# the model reported in the paper 
comp_fit1 = glmer(resp_post_reg ~ 
    1 + r_baseline_mgl_features + r_individual_gcm_features + participant_prereg_average  + 
    (1 + r_baseline_mgl_features + r_individual_gcm_features | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model without baseline mgl
comp_fit1b = glmer(resp_post_reg ~ 
    1 + r_individual_gcm_features + participant_prereg_average  + 
    (1 + r_individual_gcm_features | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model without individual gcm
comp_fit1c = glmer(resp_post_reg ~ 
    1 + r_baseline_mgl_features + participant_prereg_average  + 
    (1 + r_baseline_mgl_features | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model with individual mgl
comp_fit1d = glmer(resp_post_reg ~ 
    1 + r_baseline_mgl_features + r_individual_gcm_features + r_individual_mgl_features + participant_prereg_average  + 
    (1 + r_baseline_mgl_features + r_individual_gcm_features | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model with celex gcm
comp_fit1e = glmer(resp_post_reg ~ 
    1 + r_baseline_mgl_features + r_individual_gcm_features + r_baseline_gcm_features + participant_prereg_average  + 
    (1 + r_baseline_mgl_features + r_individual_gcm_features | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

@@

Figure \ref{bigfigure} shows how baseline and post-test regularisation means of words compare for participant responses, the GCM, and the MGL.

@@

# same for gcm weights. 
second_panel = test2 %>% 
  dplyr::group_by(
    word,
    bot_lexical_typicality,
    r_baseline_gcm_features
  ) %>% 
  dplyr::rename(
    baseline = r_baseline_gcm_features
  ) %>% 
  dplyr::summarise(
    posttest = mean(r_individual_gcm_features)
  ) %>% 
  dplyr::mutate(
    type = 'GCM'
  )

# same for MGL weights
third_panel = test2 %>% 
  dplyr::group_by(
    word,
    bot_lexical_typicality,
    r_baseline_mgl_features
  ) %>% 
  dplyr::rename(
    baseline = r_baseline_mgl_features
  ) %>% 
  dplyr::summarise(
    posttest = mean(r_individual_mgl_features)
  ) %>% 
  dplyr::mutate(
    type = 'MGL'
  )

@@

\begin{figure}
<<model_figure2, fig=T,echo=F,eval=T, width = 12.5, height = 4, fig.margin=T, fig.align = ‘center’>>=
p1
@
\caption{Baseline and individual regularisation weights: participants, GCM, MGL}
\label{bigfigure}
\end{figure}

@@

While the loess smooths are likely slightly overfit, they show the general trend in the raw data, which is echoed in the regression analysis in the main text: the "typical" trend of baseline-post-test difference is stronger than either the "random" or "reversed" trends. These are not very much different from each other. The differences are gradual. The GCM, while generally overestimating regularity, captures this gradual shift, since verb behaviour is shifted individually in the post-test. The MGL also overestimates regularisation. Since rules affect groups of verbs, rather than individual verbs, the post-test shifts are abrupt. The "typical" trend continues climbing after a longer plateau. However, the "random" and "reversed" trends trail off, where the "reversed" trend turns negative towards the higher tail of the distribution.

>>>>

# setting up columns in baseline and post-test data
baseline = baseline %>% 
  dplyr::mutate(
    rescaled_CELEX_mgl_feature_distance = scales::rescale(baseline_mgl_features), # rescale regularity weights
    rescaled_CELEX_gcm_feature_distance = scales::rescale(baseline_gcm_features),
  )

test2 = test2 %>% 
  dplyr::mutate(
    verb_baseline_average = baseline_av - mean(baseline_av, na.rm = T), # center verb average
    participant_prereg_average = pre_reg_av - mean(pre_reg_av, na.rm = T), # center participant average
    bot_lexical_typicality = dplyr::case_when( # set factor levels used in paper, order factor
        lex_typicality == 'typical' ~ 'typical',
        lex_typicality == 'random' ~ 'random',
        lex_typicality == 'atypical' ~ 'reversed'
      ) %>% 
      factor(levels = c('typical', 'random', 'reversed')),
    bot_regularisation_rate = reg_rate %>% # order factor
      factor(levels = c('nc', '-40%', '+40%')),
    rescaled_CELEX_mgl_feature_distance = scales::rescale(baseline_mgl_features), # scale regular weights
    rescaled_CELEX_gcm_feature_distance = scales::rescale(baseline_gcm_features),
    rescaled_individual_mgl_feature_distance = scales::rescale(individual_mgl_features),
    rescaled_individual_gcm_feature_distance = scales::rescale(individual_gcm_features),
    gcm_score_diff = rescaled_individual_gcm_feature_distance - rescaled_CELEX_gcm_feature_distance, # calculate score diff
    mgl_score_diff = rescaled_individual_mgl_feature_distance - rescaled_CELEX_mgl_feature_distance
  )

@@

Sections (\ref{appendixgcm}) and (\ref{appendixmgl}) also appear in the main text of  R\'acz et al. (2020), as Appendices A and B. However, this material is included here so that this Supplement can serve as a standalone document for readers who are interested in the technical details of our study. Additional material is reproduced from the main text, revisiting specific regression model summaries and additional methods we used to investigate contributions from the GCM and MGL.

@@

splive_gcm = test2 %>% 
  dplyr::filter(word == 'splive') %>% 
  dplyr::pull(rescaled_CELEX_gcm_feature_distance) %>% 
  unique %>% 
  round(2)

@@

test2 %>% 
  dplyr::filter(word == 'splive') %>% 
  dplyr::select(baseline_mgl_features,rescaled_CELEX_mgl_feature_distance) %>% 
  dplyr::distinct()

@@

In the model in Table 5 in the main text, repeated here as Table \ref{regressiontable1}, we elect to mean center continuous variables to counteract collinearity that becomes evident when including the interaction between and {\em lexical typicality}\footnote{In the SI, all p values rounded to 0.00 should be taken to indicate p $<$ 0.001.}.  Although some debate exists regarding the practice of transforming variables \citep{belsley1991conditioning,echambadi2007mean}, centering variables is common practice to remove nonessential ill conditioning, that is, relationships that inevitably exist between main and product terms \citep{aiken1991multiple,jaccard2003interaction, jaeger2008categorical}. We note that if {\em verb baseline mean} is {\em not} centered, collinearity is high (VIF=15.79) in this model. A non-centered model also yields a significant main effect for {\em lexical typicality}, with increased post-test regularization in the random and reversed conditions. However, we elect to take a more conservative approach by not including a potentially spurious main effect. Note that other than this main effect difference, models with and without centering yield results that are qualitatively indistinguishable; all other main effects and interactions are present in either case. The collinearity for the centered model (Table 5 in the main text) is acceptable, with a maximum VIF score of 2.9.

@@

We fit the \textsc{Celex-GCM} and the \textsc{Celex-MGL} on the baseline data to see how well they predict regularization responses by the baseline participants. The \textsc{Celex-MGL} outperforms the \textsc{Celex-GCM}, if slightly. Both models contribute independently to explaining variation in the data.

@@

C_CELEX_mgl_features = with(baseline, Hmisc::somers2(rescaled_CELEX_mgl_feature_distance,regular)['C']) %>% 
  round(3)
C_CELEX_gcm_features = with(baseline, Hmisc::somers2(rescaled_CELEX_gcm_feature_distance,regular)['C']) %>% 
  round(3)

# get correlation between mgl and gcm scores in baseline
mgl_gcm_cor = baseline %>% 
  dplyr::distinct(word,rescaled_CELEX_mgl_feature_distance,baseline_gcm_features) %>% 
  dplyr::summarise(
    cor = cor(rescaled_CELEX_mgl_feature_distance,baseline_gcm_features)
  ) %>% 
  dplyr::pull() %>% 
  round(3)

@@

The concordance indices of the \textsc{Celex}-MGL (\Sexpr{C_CELEX_mgl_features}) and the \textsc{Celex}-MGL (\Sexpr{C_CELEX_gcm_features}) on the baseline data are similar, with some edge retained by the MGL, as in the case of \citep{albright2003rules}. Our concordance indices are calculated using the somers2 function in R's \texttt{Hmisc} package \citep{harrell2014hmisc}.

@@

# simple baseline words data frame
baseline_words = baseline %>% 
  dplyr::distinct(word, rescaled_CELEX_mgl_feature_distance, rescaled_CELEX_gcm_feature_distance)

# fitting models 1 and 2 on it
celex_m1 = lm(rescaled_CELEX_gcm_feature_distance ~ 1 + rescaled_CELEX_mgl_feature_distance, data = baseline_words)
celex_m2 = lm(rescaled_CELEX_mgl_feature_distance ~ 1 + rescaled_CELEX_gcm_feature_distance, data = baseline_words)

# getting residuals from models and putting them back in this data frame
baseline_words = baseline_words %>% 
  dplyr::mutate(
    rescaled_CELEX_gcm_feature_distance_residual = resid(celex_m1),
    rescaled_CELEX_mgl_feature_distance_residual = resid(celex_m2)
  )

# joining it with entire baseline data
baseline = left_join(baseline, baseline_words, by = c("word", "rescaled_CELEX_mgl_feature_distance", "rescaled_CELEX_gcm_feature_distance"))

# fitting models 3 and 4
celex_m3 = glmer(regular ~ 
                1 + rescaled_CELEX_mgl_feature_distance + rescaled_CELEX_gcm_feature_distance_residual + 
                (1 + rescaled_CELEX_mgl_feature_distance + rescaled_CELEX_gcm_feature_distance_residual | subject), 
                data = baseline, 
                family = binomial ( link = logit ),
                control=glmerControl(optimizer="bobyqa"))

celex_m4 = glmer(regular ~ 
                1 + rescaled_CELEX_gcm_feature_distance + rescaled_CELEX_mgl_feature_distance_residual + 
                (1 + rescaled_CELEX_gcm_feature_distance + rescaled_CELEX_mgl_feature_distance_residual | subject), 
                data = baseline, 
                family = binomial ( link = logit ),
                control=glmerControl(optimizer="bobyqa"))

@@

<<celex_resid1, echo=F,eval=T, results=tex>>=
load('models/si_celex_m3.rda')
print(xtable::xtable(summary(celex_m3)$coef, digits = 3, label = 'resid1', caption = 'Model 3: MGL scores and GCM residuals, baseline data'))
@

<<celex_resid2, echo=F,eval=T, results=tex>>=
load('models/si_celex_m4.rda')
print(xtable::xtable(summary(celex_m4)$coef, digits = 3, label = 'resid2', caption = 'Model 4: GCM scores and MGL residuals, baseline data'))
@

@@

We fit the \textsc{Celex-GCM},the \textsc{Celex-MGL}, as well as the Individual-GCM and the Individual-MGL on the post-test data. Recall that the \textsc{Celex}-based models were trained on verbs in \textsc{Celex}. The individual-based models were trained for each participant, on \textsc{Celex} verbs as well as the co-player's responses in the ESP test. They were tested on the post-test for each participant, individually.

@@

First, we calculated concordance indices for the \textsc{Celex}- and individual-models on the post-test data of the ESP experiment.

@@

# C_CELEX_mgl_features # celex-mgl on baseline
# C_CELEX_gcm_features # celex-gcm on baseline

C_test2_baseline_mgl_features = with(test2, Hmisc::somers2(rescaled_CELEX_mgl_feature_distance,resp_post_reg)['C']) %>% round(3)
C_test2_baseline_gcm_features = with(test2, Hmisc::somers2(rescaled_CELEX_gcm_feature_distance,resp_post_reg)['C']) %>% round(3)
C_test2_individual_mgl_features = with(test2, Hmisc::somers2(rescaled_individual_mgl_feature_distance,resp_post_reg)['C']) %>% round(3)
C_test2_individual_gcm_features = with(test2, Hmisc::somers2(rescaled_individual_gcm_feature_distance,resp_post_reg)['C']) %>% round(3)

@@

Table \ref{modellingsummary} summarizes the concordance indices between our data and the various categorization models. The \textsc{Celex}-MGL outperforms the \textsc{Celex}-GCM on the post-test data to some extent, much like in the case of our baseline data. The individual-GCM considerably improves on the \textsc{Celex}-GCM in terms of explaining the post-test data. The individual-MGL also improves on the \textsc{Celex}-MGL, but to a lesser extent.

@@

    \centering
    \begin{tabular}{lllll}
            & training data & method & test data & C\\
            \hline
\textsc{Celex}-GCM & real verbs & `analogy' & verbs in baseline &\Sexpr{C_CELEX_gcm_features }\\
\textsc{Celex}-MGL & real verbs & `rules' & verbs in baseline &\Sexpr{C_CELEX_mgl_features }\\ \hline
\textsc{Celex}-GCM & real verbs & `analogy' & verbs in post-test &\Sexpr{C_test2_baseline_gcm_features}\\
individual-GCM & real verbs + verbs seen in ESP & `analogy' & verbs in post-test &\Sexpr{C_test2_individual_gcm_features}\\

@@

indiv_m5 = glmer(resp_post_reg ~
    1 + rescaled_CELEX_gcm_feature_distance + gcm_score_diff + participant_prereg_average + 
    (1 + rescaled_CELEX_gcm_feature_distance + gcm_score_diff | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

@@

indiv_m6 = glmer(resp_post_reg ~ 
    1 + rescaled_CELEX_mgl_feature_distance + mgl_score_diff + participant_prereg_average  + 
    (1 + rescaled_CELEX_mgl_feature_distance + mgl_score_diff | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

@@

load('models/si_indiv_m5.rda')
print(xtable::xtable(summary(indiv_m5)$coef, digits = 3, label = 'indiv1', caption = 'Model 5: Celex-GCM and individual score difference, post-test data'))

@@

<<indiv_diff2, echo=F,eval=T, results=tex>>=
load('models/si_indiv_m6.rda')
print(xtable::xtable(summary(indiv_m6)$coef, digits = 3, label = 'indiv2', caption = 'Model 6: Celex-MGL and individual score difference, post-test data'))
@

@@

# the model reported in the paper 
comp_fit1 = glmer(resp_post_reg ~ 
    1 + rescaled_CELEX_mgl_feature_distance + rescaled_individual_gcm_feature_distance + participant_prereg_average  + 
    (1 + rescaled_CELEX_mgl_feature_distance + rescaled_individual_gcm_feature_distance | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model without baseline mgl
comp_fit1b = glmer(resp_post_reg ~ 
    1 + rescaled_individual_gcm_feature_distance + participant_prereg_average  + 
    (1 + rescaled_individual_gcm_feature_distance | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model without individual gcm
comp_fit1c = glmer(resp_post_reg ~ 
    1 + rescaled_CELEX_mgl_feature_distance + participant_prereg_average  + 
    (1 + rescaled_CELEX_mgl_feature_distance | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model with individual mgl
comp_fit1d = glmer(resp_post_reg ~ 
    1 + rescaled_CELEX_mgl_feature_distance + rescaled_individual_gcm_feature_distance + rescaled_individual_mgl_feature_distance + participant_prereg_average  + 
    (1 + rescaled_CELEX_mgl_feature_distance + rescaled_individual_gcm_feature_distance | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

# model with celex gcm
comp_fit1e = glmer(resp_post_reg ~ 
    1 + rescaled_CELEX_mgl_feature_distance + rescaled_individual_gcm_feature_distance + rescaled_CELEX_gcm_feature_distance + participant_prereg_average  + 
    (1 + rescaled_CELEX_mgl_feature_distance + rescaled_individual_gcm_feature_distance | participant_id) + (1 | word), 
                 data = test2, 
                 family = binomial (link = logit), 
                 control=glmerControl(optimizer="bobyqa"))

@@

Figure \ref{bigfigure} shows how baseline and post-test regularization means of words compare for participant responses, the GCM, and the MGL.

@@

# same for gcm weights. 
second_panel = test2 %>% 
  dplyr::group_by(
    word,
    bot_lexical_typicality,
    rescaled_CELEX_gcm_feature_distance
  ) %>% 
  dplyr::rename(
    baseline = rescaled_CELEX_gcm_feature_distance
  ) %>% 
  dplyr::summarise(
    posttest = mean(rescaled_individual_gcm_feature_distance)
  ) %>% 
  dplyr::mutate(
    type = 'GCM'
  )

# same for MGL weights
third_panel = test2 %>% 
  dplyr::group_by(
    word,
    bot_lexical_typicality,
    rescaled_CELEX_mgl_feature_distance
  ) %>% 
  dplyr::rename(
    baseline = rescaled_CELEX_mgl_feature_distance
  ) %>% 
  dplyr::summarise(
    posttest = mean(rescaled_individual_mgl_feature_distance)
  ) %>% 
  dplyr::mutate(
    type = 'MGL'
  )

@@

\begin{figure}
<<model_figure2, fig=T,echo=F,eval=T, width = 12.5, height = 4, fig.margin=T, fig.align = ‘center’>>=
p1
@
\caption{Baseline and individual regularization weights: participants, GCM, MGL}
\label{bigfigure}
\end{figure}

@@

While the loess smooths are likely slightly overfit, they show the general trend in the raw data, which is echoed in the regression analysis in the main text: the `typical' trend of baseline-post-test difference is stronger than either the "random" or "reversed" trends. These are not very much different from each other. The differences are gradual. The GCM, while generally overestimating regularity, captures this gradual shift, since verb behavior is shifted individually in the post-test. The MGL also overestimates regularization. Since rules affect groups of verbs, rather than individual verbs, the post-test shifts are abrupt. The "typical" trend continues climbing after a longer plateau. However, the `random' and `reversed' trends trail off, where the "reversed" trend turns negative towards the higher tail of the distribution.
